Reasoning About a Machine with Local Capabilities

### 2018-01-18 esop-2018/paper.tex
changed acks to subsubsection

\section*{Acknowledgements}
This research was supported in part by the ModuRes Sapere Aude Advanced Grant
from The Danish Council for Independent Research for the Natural Sciences (FNU).

>>>>

\subsubsection*{Acknowledgements.}
This research was supported in part by the ModuRes Sapere Aude Advanced Grant
from The Danish Council for Independent Research for the Natural Sciences (FNU).
